##################################################################
# Sept 24, 2022
# Shivangi Deepak Mewada 'sm4956'
##################################################################

---
title: "p8105 HW1"
output: github_document
---

```{r}
library(tidyverse)
```

# Problem 1
## Part 1

```{r loading dataset penguins}
data("penguins", package = "palmerpenguins")
```

```{r description of penguins dataset}
penguins_df = data.frame(penguins)
nrow(penguins_df)
ncol(penguins_df)
mean(penguins_df$flipper_length_mm, na.rm = TRUE)
```

## 1a. Data in dataset 'Penguins':  
### Names of important variables: Species, Island, Bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, year. 
* There are 3 'species' of penguins: Adelie, Chinstrap and Gentoo. 
* There are 3 'islands': Torgersen, Bisco and Dream. These are both character variables. 
* 'bill_length_mm' provides the length of bills of penguins in mm. 
* 'bill_depth_mm' provides the depth of bills of penguins in mm. 
* 'flipper_length_mm' provides length of flippers of penguins in mm. 
* 'body_mass_g' provides the body mass information of penguins in grams. These are all numeric variables. 
* 'sex' and 'year' provide information about the sex (dichotomous variable: Male and Female) and year of birth of penguins.

## 1b. Size of the dataset:
### the dataset 'Penguins' has 344 rows, i.e. 344 observations, and 8 columns, i.e, 8 variables.

## 1c. mean flipper length:
### the mean flipper length is 200.9152 mm

# Problem 1
## Part 2

```{r scatterplot for Penguins}
ggplot(penguins_df,aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave("scatter_penguins_df.pdf", height = 6, width = 6)

```

# Problem 2
## Part 1: creating data frame HW1P2

```{r problem 2 dataframe creation}
HW1P2_df = 
  tibble (
    var_numeric = rnorm (n = 10),
    vec_log = var_numeric > 0,
    vec_char = c("Elena","Damon","Stefan","Caroline","Katherine","Tyler","Matt","Bonnie","Klaus","Elijah"),
    vec_factor = factor(c("she","he","he","she","they","he","they","she","he","they"))
  )
```

## Part 2: Means of variables

```{r mean of numeric variable}
mean_var_numeric = mean(pull(HW1P2_df, var_numeric))
round(mean_var_numeric, digits = 2)
```
### mean of var_numeric works because it is numerical.


```{r mean of logical vector}
mean_vec_log = mean(pull(HW1P2_df, vec_log))
round(mean_vec_log, digits = 2)
```
### mean of vec_log works because it is a logical variable.

```{r mean of character vector}
mean_vec_char = mean(pull(HW1P2_df, vec_char))
round(mean_vec_char, digits = 2)
```
### Mean of vec_char doesn't work because it is not numeric or logical. Value is NA.

```{r mean of factor vector}
mean_vec_factor = mean(pull(HW1P2_df, vec_factor))
round(mean_vec_factor, digits = 2)
```
### Mean of vec_factor doesn't work because it is not numeric or logical. Value is NA.

